Chemistry of fossil Pinus pollen and the effect of acetolysis

### 2021-03-24 manuscript.Rmd
testing spls; started writing bootstrap cv file

RQs
i. Difference between fresh and fossil grains.
i.i effect of orientation on chemistry
i.ii effect of depth/age on chemistry
ii Differences between cores

>>>>

RQs
i. Differences between cores
ii.i Difference between acetolysed and fossil
ii.ii Difference between fresh and fossil grains.
iii effect of depth/age on chemistry

iv effect of orientation on chemistry
